Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Saturn-Sized Planet in IC~2602

### 2020-07-08 paper/ms.tex
fix typos

In ``Method 1'', we measured spectroscopic parameters from each of the
CHIRON spectra (Section~\ref{subsec:chiron}).
We then calculated the stellar radius and reddening
following \citet{stassun_accurate_2017}.  We first derived the
bolometric flux by combining available broadband magnitudes from Gaia,
Tycho-2, APASS, 2MASS, and WISE.  We then fitted the SED with the
\citet{kurucz_atlas12_2013} stellar atmopshere models, and summed to
find $F_{\rm bol}$.  When fitting the atmosphere model, we varied the
extinction ($A_{\rm V}$) and the overall normalization.  This
procedure yielded $A_{\rm V} = 0.20\pm0.03$, which agrees with the
average from the \cn\ isochrone fits of \citet{randich_gaiaeso_2018}.
Combining the spectroscopic effective temperature, bolometric flux,
and Gaia distance, we determined the stellar radius using the
Stefan-Boltzmann law.  Combining this radius the spectroscopic $\log
g$ also yields a stellar mass.

@@

The posteriors from this procedure are given in
Table~\ref{tab:posterior}.  The transit is grazing.  In the absence of
a strong prior on the stellar density, the grazing geometry would
hinder our ability to infer the planet-to-star size ratio.  However,
our prior on the stellar parameters from the cluster isochrone fit is
strong enough that we can derive two-sided limits on the
planet-to-star size ratio.  The relevant posterior probabilities are
shown in Figure~\ref{fig:subsetcorner}.

@@

\tn\ joins a number of other young planetary systems reported from
TESS, including DS~Tuc~Ab, HIP~67522b, TOI~1726, and AU~Mic~b
\citep{newton_tess_2019,zhou_well_2019,montet_young_2019,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}
Unlike these planets, \pn\ is validated but not yet
confirmed.

@@

The Rossiter-McLaughlin approach is more likely to yield short-term
success than a direct mass measurement because of the RV noise
expected to be induced by stellar rotation.  The photometric amplitude
induced by starspots on \tn\ is $\approx 2\%$. 
The RV noise expected over the course of the $\approx 3\,{\rm d}$
rotation period can then be estimated by multiplying the photometric amplitude and
spectroscopic equatorial velocity.  This gives $\sigma_{\rm RV,rot}
\approx 300\,{\rm m\,s}^{-1}$, and is consistent with the scatter we
observe in our radial velocities from FEROS.  Detecting
a planet's Doppler signal in these regimes is
challenging, and requires a significant amount of data and care in
signal extraction \citep{barragan_radial_2019}.  The
Rossiter-McLaughlin measurement avoids the majority of this issue
because the transit occurs over a much shorter duration than a single
stellar rotation period.

If the RM measurements prove that the planet
is real, a campaign to measure the mass timed to coincide with
TESS sectors 36 and 37 ({\it i.e.}, from late March to late May of
2021) would significantly ease the extraction of the planetary Doppler
signal.  The reason is that the radial velocities, activity
indicators, and photometry could then be modeled simultaneously, which
would greatly constrain any Gaussian process model for the
spot-induced RV signal.

>>>>

In ``Method 1'', we measured spectroscopic parameters from each of the
CHIRON spectra (Section~\ref{subsec:chiron}).
We then calculated the stellar radius and reddening
following \citet{stassun_accurate_2017}.  We first derived the
bolometric flux by combining available broadband magnitudes from Gaia,
Tycho-2, APASS, 2MASS, and WISE.  We then fitted the SED with the
\citet{kurucz_atlas12_2013} stellar atmopshere models, and summed to
find $F_{\rm bol}$.  When fitting the atmosphere model, we varied the
extinction ($A_{\rm V}$) and the overall normalization.  This
procedure yielded $A_{\rm V} = 0.20\pm0.03$, which agrees with the
average from the \cn\ isochrone fits of \citet{randich_gaiaeso_2018}.
Combining the spectroscopic effective temperature, bolometric flux,
and Gaia distance, we determined the stellar radius using the
Stefan-Boltzmann law.  Combining this radius with the spectroscopic
$\log g$ also yields a stellar mass.

@@

The posteriors from this procedure are given in
Table~\ref{tab:posterior}.  The transit is grazing.  In the absence of
a strong prior on the stellar density, the grazing geometry would
hinder our ability to infer the planet-to-star size ratio.  However,
our priors on the stellar parameters from the cluster isochrone fit
are strong enough that we can derive two-sided limits on the
planet-to-star size ratio.  The relevant posterior probabilities are
shown in Figure~\ref{fig:subsetcorner}.

@@

\tn\ joins a number of other young planetary systems reported from
TESS, including DS~Tuc~Ab, HIP~67522b, TOI~1726, and AU~Mic~b
\citep{newton_tess_2019,zhou_well_2019,montet_young_2019,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}.
Unlike these planets, \pn\ is validated but not yet
confirmed.

@@

The Rossiter-McLaughlin approach is more likely to yield short-term
success than a direct mass measurement because of the RV noise
expected to be induced by stellar rotation.  The photometric amplitude
induced by starspots on \tn\ is $\approx 2\%$.  The spot-induced RV
variation expected over the course of the $\approx 3\,{\rm d}$
rotation period can then be estimated by multiplying the photometric
amplitude and spectroscopic equatorial velocity.  This gives
$\sigma_{\rm RV,rot} \approx 300\,{\rm m\,s}^{-1}$, and is consistent
with the scatter we observe in our radial velocities from FEROS.
Detecting a planet's Doppler signal in these regimes is challenging,
and requires a significant amount of data and care in signal
extraction \citep{barragan_radial_2019}.  The Rossiter-McLaughlin
measurement avoids the majority of this issue because the transit
occurs over a much shorter duration than a single stellar rotation
period.

If the RM measurements prove that the planet
is real, a campaign to measure the mass timed to coincide with
TESS sectors 36 and 37 ({\it i.e.}, from late March to late May of
2021) would significantly ease the extraction of the planetary Doppler
signal.  The reason is that the radial velocities, activity
indicators, and photometry could then be modeled simultaneously, which
would greatly constrain a Gaussian process model for the
spot-induced RV signal.
